Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-10 lloveras_2020_Albert.tex
Nueva Section 2.3, 3.1 y 3.2, by Albert

\begin{abstract}
Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24. Tomographic reconstructions and results of the model are analyzed in distinct coronal magnetic structures. We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it. We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.

@@

For the two targeted rotations, DEMT and AWSoM results were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them. To that end four different types of {legs} corresponding with four different types of magnetic structures were selected:
%\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\

@@

\end{itemize}
\diego{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} \notebyalbert{Charlemos los tres en persona de esto.}

@@

\albert{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}\albert{, and the measure $R$ was calculated by means of Equation (\ref{R}).}}

{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights \albert{of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), \albert{the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the \albert{open/closed boundaries of the magnetic field of the} AWSoM model.

@@

Target CR-2082 was highly axisymmetric (i.e, \albert{characterized by} a high azymuthal symmetry) and showed two \albert{small} ARs (active \albert{regions), both near latitude} $+30\mdeg$ and \albert{around longitudes} $50\mdeg$ and $120\mdeg$\albert{, respectively}. Target CR-2208 was \albert{considerably less axisymmetric and} showed two \albert{ARs, both near latitude} $+5\mdeg$ and \albert{around longitudes $140\mdeg$ and $300\mdeg$, respectively.}

\albert{The magnetically open and closed regions of the AWSoM model are associated to CHs and the the equatorial streamer belt, respectively. Consistently with that, the open/closed boundaries derived from the respective AWSoM model quite accurately match the regions which exhibit the strongest latitudinal gradient in the DEMT maps of both the electron density and temperature.}

@@

\albert{Visual inspection of Figures \ref{momento1} and \ref{momento2} shows that the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs. They also that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between \albert{SCs 24 and 25}, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to \albert{increase with height}. A similar behaviour is seen in CR-2208, belonging to the declining phase of \albert{SC 25, but having a much less axisymmetric structure this characteristic is not so obvious. This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.

\albert{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of DEMT measure $R$ defined by Equation (\ref{R}), at the same three heighs shown in Figures \ref{momento1} and \ref{momento2}. In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$. The notable exception is to be found in the CHs of the target rotation analyzed based on AIA data. A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}. This point is further discussed below.}

@@

\albert{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model. For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected. For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}. {As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR2082 (left) and CR2208 (right). \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.}}
\label{rpoint_demt}
\end{center}
\end{figure}

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in grey color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, \albert{magenta and cyan} color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III. On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.} \notebyalbert{Los números deben ser actualizados, o la frase eliminada.}

{Type 0 (small down) legs mainly populate the equatorial latitudes. This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level \albert{around the solar minimum beween SCs 24 and 25} by \citet{nuevo_2013}. Later on, \citet{lloveras_2017} showed \albert{that} equatorial down loops in streamers were also to be found in the deep minimum between SCs \albert{23 and 24}. Here, we verify the existence of this type of structure for the two target rotations. The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}. Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt. Finally, type III (open) legs populate of course the CHs.}

%\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
\label{gradt_demt}
\end{center}
\end{figure}

Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III. The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs. For both rotations, \albert{the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.

\albert{The notable difference between both rotations is the characteristic \albert{value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208. This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208. In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy. Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, shows that in most of the CH region the results for $\Tm$ below height $1.105\,\mrsun$ are quite uniform and artificially low. As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable. As a result, the temperature gradient along these legs is artificially larger, with the linear fit trying to simultaneously fit the artificially low values of $\Tm$ at lower heights. In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis. We will return to this point in the conclusion section.}

%\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}

%\temp{ Comentar en la discusion el paper de shift y cramer, para decir un poco sobre los down y la incapacidad del modelo en reproducirlos}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR-2082 and CR-2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.} }
\label{histos_fulldemt}
\end{center}
\end{figure}

\albert{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by field line type}. From top to bottom {results are shown for} type 0 to type III {field lines}\albert{, respectively}. From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.

\albert{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}. For CR-2082 quantities are expressed as absoulte values, {while} for CR-2208 they are informed {as a precentual variation} relative to the corresponding results for CR-2082. \albert{The following major results, both concerning the structure of each rotation individually as well as their comparison, can be drawn.}

@@

\albert{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature. In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}

@@

%To establish if the differences in the results between the two rotations are significant, Section \ref{uncertainties} estimates the error bars due the dominating systematic uncertainties.
%\diego{quizas vale la pena introducir alguna comparacion sobre el campo magnetico, veremos como quedan los comentarios de ceci.}
%{Also, within the streamer belt the magnetic field strength is similar in both rotations in the northern hemisphere, while in the southern hemisphere CR-1915 exhibits $10-80\%$ larger values compared to CR-2081, with increasing difference for larger latitudes. In the coronal holes, the magnetic field strength of CR-1915 is much larger than for CR-2081, exhibiting values up to 50\% larger in the northern hemisphere and more than twice larger in the southern hemisphere.}

%Previous works have found magnetic loops which temperature decrease with height, most generally in equatorial latitudes \citep{huang_2012,nuevo_2013}. This type of loops with negative gradients produce a negative conductive flux that contribute to the heating in the corona. In this work, we compute the loop-integrated energy quantities separately in three different populations of loops.

\albert{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop). \albert{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}

@@

\albert{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0. This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0. As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterised by the relatively largest values of electron density. Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$. According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by \albert{values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}

{In the case of the quantity $\phi_c$, its sign depends on that of the conductive flux $F_c$. As shown in \citet{maccormack_2017}, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, which is verified in Figure \ref{energia_demt}.}

>>>>

\begin{abstract}
Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24. Tomographic reconstructions and results of the model are \albert{analysed} in distinct coronal magnetic structures. We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it. We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.

@@

\albert{Coronal magnetic structures for which their temperature increases/decreases with height (in the inner corona) have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}

\albert{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model. Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}

\diego{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} \notebyalbert{Charlemos los tres en persona de esto.}

@@

\end{itemize}

\albert{In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.}

@@

{As described in Section \ref{demt}, we carried out DEMT reconstructions of the coronal structure for target rotations CR-2082 and CR-2208 using STEREO/EUVI and SDO/AIA data, respectively.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}{, and the measure $R$ was calculated by means of Equation (\ref{R}).}}

{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model.

@@

\albert{Both target rotations are highly axisymmetric, i.e. characterized by a high azymuthal symmetry. Rotation CR-2082} showed two {small} ARs (active {regions), both near latitude} $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}. \albert{Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}

{The magnetically open and closed regions of the AWSoM model are associated to CHs and the the equatorial streamer belt, respectively. Consistently with that, the \albert{location of the} open/closed boundaries derived from the respective AWSoM model quite accurately match \albert{the regions of the DEMT maps which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}

@@

{\albert{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs. They also that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the \albert{the low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behaviour is seen in CR-2208, belonging to the declining phase of {SC 25, but having a \albert{somewhat less axisymmetric} structure this characteristic is not so obvious. This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.

{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of \albert{the DEMT} measure $R$ defined by Equation (\ref{R}), at the same three heighs shown in Figures \ref{momento1} and \ref{momento2}. In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$. The notable exception is to be found in the CHs of the target rotation \albert{analysed} based on AIA data. A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}. This point is further discussed below.}

@@

{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model. For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected. For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}. {As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR2082 (left) and CR2208 (right). \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. \albert{The location of} type 0, I, II and III legs \albert{is shown} in blue, red, \albert{magenta and cyan} color, respectively.}}
\label{rpoint_demt}
\end{center}
\end{figure}

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in grey color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III. On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.} \notebyalbert{Los números deben ser actualizados, o la frase eliminada.}

{Type 0 (small down) legs mainly populate the equatorial latitudes. This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum beween SCs 24 and 25} by \citet{nuevo_2013}. Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}. Here, we verify the existence of this type of structure for the two target rotations. The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}. Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt. Finally, type III (open) legs populate of course the CHs.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
\caption{Frequency histograms of the temperature radial gradient for \albert{the four types of legs} in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
\label{gradt_demt}
\end{center}
\end{figure}

Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III. The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs. For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.

{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208. This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208. In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy. Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, \albert{reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is quite uniform and artificially low}. As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable. As a result, the temperature gradient along these legs is artificially larger, with the linear fit trying to simultaneously fit the artificially low values of $\Tm$ at lower heights. In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis. We will return to this point in the conclusion section.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{{Statistical distribution of \albert{DEMT results for rotations CR-2082 (blue) and CR-2208 (red)} traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: \albert{electron density $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$,} electron density scale height $\lN$, \albert{and loop-averaged temperature $\aTm$. In each panel} the median value $m$ is indicated.} }
\label{histos_fulldemt}
\end{center}
\end{figure}

{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by field line type}. From top to bottom {results are shown for} type 0 to type III {field lines}{, respectively}. From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.

{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}. For CR-2082 quantities are expressed as absoulte values, {while} for CR-2208 they are informed {as a precentual variation} relative to the corresponding results for CR-2082. {The following major results, both concerning the structure of each rotation individually as well as their comparison, can be drawn.}

@@

{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, progressively exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature. In both rotations also, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}

@@

{To analyze the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop). {For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}

@@

{For both rotations, the value of the \albert{loop-integrated} radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0. This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0. As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterised by \albert{the largest} values of electron density. Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$. According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by {values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}

{\albert{The sign of the quantity $\phi_c$ depends on that of the conductive flux $F_c$. Equations (\ref{Fc}) and (\ref{phi_c}) imply that } down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, \albert{as verified} in Figure \ref{energia_demt}.}

{\albert{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of \albert{loop, matching the values reported by} \citet{maccormack_2017}. Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, \albert{this affects only the smallest sized loops of the type 0}, and it is \albert{most probably} due to the limited temperature sensitivity of the instrumental passbands. The radiative loss term is \albert{here calculated based on plasma emission detected by three coronal bands of EUVI or AIA. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely understimated, leading to values $\phi_h<0$ in loops of type 0, \albert{being characterized} by $\phi_c<0$.}
